Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Plurality
Correct tank length

Static foil performance does not tell the whole story for a cross-flow turbine.
The azimuthal, and therefore temporal variation of $\alpha$ in a cross-flow
turbine implies dynamic loading, encountering dynamic stall for tip speed ratios
near and below those of maximum rotor torque \cite{Para2002}. Bousman
\cite{Bousman2000-evaluation} states that dynamic stall is relatively
insensitive to Reynolds number for $Re=1.0 \times 10^5$--$2.5 \times
10^5$---judging from measurements on a pitching VR-7 foil in a wind and water
tunnel---since the loading is dominated by vortex shedding. However, Singleton
and Yeager Jr. \cite{Singleton2000} state that Reynolds number effects on
dynamic stall remains an unsolved question.

@@

Experiments were performed in a turbine test bed specifically designed for
cross-flow turbines. The test bed was integrated as part of the UNH tow tank,
which is a 30 m long facility with a 3.66 m wide and 2.44 m deep cross-section.
The turbine model used in this study was the UNH Reference Vertical Axis Turbine
(RVAT), which was designed to be a generic case for numerical model testing,
similar to the Sandia National Labs/US Department of Energy RM2 River Turbine
\cite{Neary2014}, but with higher solidity, or blade chord-to-radius ratio.

>>>>

Static foil performance does not tell the whole story for a cross-flow turbine.
The azimuthal, and therefore temporal variation of $\alpha$ in a cross-flow
turbine implies dynamic loading, encountering dynamic stall for tip speed ratios
near and below those of maximum rotor torque \cite{Para2002}. Bousman
\cite{Bousman2000-evaluation} states that dynamic stall is relatively
insensitive to Reynolds number for $Re=1.0 \times 10^5$--$2.5 \times
10^5$---judging from measurements on a pitching VR-7 foil in a wind and water
tunnel---since the loading is dominated by vortex shedding. However, Singleton
and Yeager Jr. \cite{Singleton2000} state that the effect of Reynolds number on
dynamic stall remains an unsolved question.

@@

Experiments were performed in a turbine test bed specifically designed for
cross-flow turbines. The test bed was integrated as part of the UNH tow tank,
which is a 36 m long facility with a 3.66 m wide and 2.44 m deep cross-section.
The turbine model used in this study was the UNH Reference Vertical Axis Turbine
(RVAT), which was designed to be a generic case for numerical model testing,
similar to the Sandia National Labs/US Department of Energy RM2 River Turbine
\cite{Neary2014}, but with higher solidity, or blade chord-to-radius ratio.
